Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-23 article/draft.tex
typos in the Twitter section about flags

Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center. At the tweet level, notices take the form of a label or an interstitial. Labels are context specific (e.g. COVID-19 or presidential elections) and  redirect users to a webpage to get more context, for example {\it Get the facts about COVID-19'} (see right panel of figure \ref{fig8}). Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts, for example {\it The following media includes potentially sensitive content} (see left panel of figure \ref{fig_notice}). At the account level, notices can also indicate whether an account has been temporarily or permanently suspended.

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
   	 %\end{multicols}
	%\begin{multicols}{1} 
		\includegraphics[scale=0.32]{./img/tweets/Capture_2021-06-30.png}
	%\end{multicols}
	\caption{Two tweets sharing the same link marked as False by Science Feedback, screenshots taken on June $20$, 2021. Left Panel: Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label. Right Panel: Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
	\label{fig8}
\end{figure}

@@

To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet contains a notice or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API. Hence, in order to investigate the presence of labels of all types, we resorted to scrape Twitter data using Minet [5]. This tool was recently enriched upon our request in order to capture whether a tweet contains a notice or not, via the ``minet twitter scrape'' command.

@@

In this section, we take a deeper look at how labels and notices are introduced by Twitter, to indicate content which is inaccurate or false. To that end, we gathered a set of $3094$ links redirecting to articles which were marked as $False$ between April $2019$ and February $2021$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information. As a second step, we collected (on June $30$, $2021$) via Minet Command line tool~\cite{minet} all the tweets that have shared a link which belongs to the set of $3094$ links marked as $False$. This data collection resulted in $323$ $938$ tweets, excluding retweets. Only $28$ tweets contained the label { \it ``Get the facts about COVID-19''}, $5$ tweets contained the label {\it ``Learn about US 2020 election security efforts''} and only $1$ had the following label {\it ``This claim about election fraud is disputed''}. Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same link, among the set of collected tweets. To give an example, $657$ tweets had shared the exact same link redirecting to a video on Bitchute, entitled {\it Important information on coronavirus 5G Kung Flu}. Among those $657$ tweets only $3$ contained the notice {\it ``Get the facts about COVID-19''} (see figure \ref{fig8}). This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by other users.

\begin{figure}[h]
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png}
	%\end{multicols}
	\caption{Left Panel: Tweet containing a URL link hidden behind an interstitial. Right Panel: when clicking on $view$, to view the content hidden behind the interstitial. Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
	\label{fig_notice}
\end{figure}

@@

We further examine the placement of interstitials that indicate a possibly sensitive content. We find that only $9344$ ($2.97\%$) tweets out of $323$ $938$ containing a link marked as False, have an interstitial {\it potentially sensitive content}. To check whether the interstitial {\it potentially sensitive content} is automated or not, we pick out one tweet having shared a link marked as False\footnote{The link marked as False redirects to the article {\it 5G Technology and induction of coronavirus in skin cells – US National Library of Medicine (what David Icke has been saying for months) } and can be found \href{https://davidicke.com/2020/07/22/5g-technology-and-induction-of-coronavirus-in-skin-cells-us-national-library-of-medicine-what-david-icke-has-been-saying-for-months/}{here}.}, which also contains the interstitial {\it potentially sensitive content} (see figure \ref{fig_notice}). Then we look in the set of $323$ $938$ tweets for other tweets who have shared the exact same link. We find a total of $32$ tweets. Among those $32$ tweets only $5$ tweets had the interstitial ``potentially sensitive content''. Again this points towards the non-automation of interstitials placement. Furthermore, notice that the appearance of interstitials may depend on the settings of a user's account and country or language specific regulations. In particular, in the settings of Twitter account, one can deactivate the display of interstitials for {\it sensitive content}, by ticking the box {\it Display media that may contain sensitive content} in the section {\it content you see}.

@@

Finally, the number of tweets containing the interstitial {\it potentially sensitive content} ($9344$ tweets) widely outnumbers the tweets which contain a flag ($32$ tweets), among the set of $323$ $938$ tweets containing a link marked as False (see table \ref{flags_tab}). Furthermore, we noticed that among the tweets which contain the interstitial {\it potentially sensitive content}, there are tweets which contain links redirecting to misleading articles about COVID-19 and yet they are not marked by the flag { \it Get the facts about COVID-19}. We also noticed that the $9344$ tweets marked with the interstitial {\it potentially sensitive content} do not necessarily contain graphic violent\footnote{The Twitter Help center explains the placement of interstitials of possibly sensitive content as follows: ``We may place some forms of sensitive media like adult content or graphic violence behind an interstitial advising viewers to be aware that they will see sensitive media if they click through''.} content but rather links that redirect to articles marked as $False$ by Science Feedback. When navigating through the Twitter Help Center, we found no explanation for this large discrepancy between using the interstitial {\it potentially sensitive content} and flags which provide more context to users.\footnote{Twitter Safety account announced in a Tweet (see Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}) on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations".}

>>>>

Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center. At the tweet level, notices take the form of a label or an interstitial. Labels are context specific (e.g. COVID-19 or presidential elections) and  redirect users to a webpage to get more context, for example {\it ``Get the facts about COVID-19''} (see right panel of figure \ref{fig8}). Interstitials are presented as a greyed box on top of a tweet, which indicates sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts, for example {\it ``The following media includes potentially sensitive content''} (see left panel of figure \ref{fig_notice}). At the account level, notices can also indicate whether an account has been temporarily or permanently suspended.

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
   	 %\end{multicols}
	%\begin{multicols}{1} 
		\includegraphics[scale=0.32]{./img/tweets/Capture_2021-06-30.png}
	%\end{multicols}
	\caption{Two tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021. Left Panel: Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label. Right Panel: Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
	\label{fig8}
\end{figure}

@@

To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet contains a label or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the Twitter API v2. Hence, in order to investigate the presence of notices of all types, we resorted to scrape publicly available tweets, using Minet [5]. This tool was recently enriched upon our request in order to capture whether a tweet contains a notice or not, via the ``minet twitter scrape'' command.

@@

In this section, we take a deeper look at how labels and interstitials are introduced by Twitter, to indicate content which is inaccurate or false. To that end, we gathered a set of $3$ $094$ links redirecting to articles which were marked as ``False'' between April $2019$ and February $2021$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information. 
As a second step, we collected (on June $30$, $2021$) using Minet~\cite{minet} all the tweets that have shared a link which belongs to the set of $3$ $094$ links marked as $False$. This data collection resulted in $323$ $938$ tweets, excluding retweets. Only $28$ tweets contained the label { \it ``Get the facts about COVID-19''}, $5$ tweets contained the label {\it ``Learn about US 2020 election security efforts''} and only $1$ had the following label {\it ``This claim about election fraud is disputed''}. Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same link, among the set of collected tweets. To give an example, $657$ tweets had shared the exact same link redirecting to a video on Bitchute, entitled {\it Important information on coronavirus 5G Kung Flu}. Among those $657$ tweets only $3$ contained the label {\it ``Get the facts about COVID-19''} (see figure \ref{fig8}). This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by other users.

\begin{figure}[h]
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png}
	%\end{multicols}
	\caption{Left Panel: Tweet containing a URL link hidden behind an interstitial. Right Panel: when clicking on $view$, to view the content hidden behind the interstitial in the left panel. Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
	\label{fig_notice}
\end{figure}

@@

We further examine the placement of interstitials that indicate a possibly sensitive content. We find that only $9$ $344$ ($2.97\%$) tweets out of $323$ $938$ containing a link marked as False, have an interstitial {\it ``potentially sensitive content''}. To check whether the interstitial {\it ``potentially sensitive content''} is automated or not, we pick out one tweet having shared a link\footnote{The link marked as False redirects to the article {\it 5G Technology and induction of coronavirus in skin cells – US National Library of Medicine (what David Icke has been saying for months) } and can be found \href{https://davidicke.com/2020/07/22/5g-technology-and-induction-of-coronavirus-in-skin-cells-us-national-library-of-medicine-what-david-icke-has-been-saying-for-months/}{here}.} marked as ``False'', which also contains the interstitial {\it potentially sensitive content} (see figure \ref{fig_notice}). Then we look in the set of $323$ $938$ tweets for other tweets who have shared the exact same link. We find a total of $32$ tweets. Among those $32$ tweets only $5$ tweets had the interstitial ``potentially sensitive content''. Again this points towards the non-automation of interstitials placement. Furthermore, notice that the appearance of interstitials may depend on the settings of a user's account and country or language specific regulations. In particular, in the settings of Twitter account, one can deactivate the display of interstitials for {\it sensitive content}, by ticking the box {\it Display media that may contain sensitive content} in the section {\it content you see}.

@@

Finally, the number of tweets containing the interstitial {\it ``potentially sensitive content''} ($9$ $344$ tweets) widely outnumbers the tweets which contain a flag ($32$ tweets), among the set of $323$ $938$ tweets containing a link marked as ``False'' (see table \ref{flags_tab}). Furthermore, we noticed that among the tweets which contain the interstitial {\it ``potentially sensitive content''}, there are tweets which contain links redirecting to misleading articles about COVID-19 and yet they do not contain the label { \it ``Get the facts about COVID-19''}. We also noticed that the $9$ $344$ tweets which contain the interstitial {\it ``potentially sensitive content''} do not necessarily contain graphic violent content\footnote{The Twitter Help center explains the placement of interstitials of possibly sensitive content as follows: ``We may place some forms of sensitive media like adult content or graphic violence behind an interstitial advising viewers to be aware that they will see sensitive media if they click through''.} but rather links that redirect to articles marked as ``False'' by Science Feedback. When navigating through the Twitter Help Center, we found no explanation for this large discrepancy between using the interstitial {\it ``potentially sensitive content''} and labels which provide more context to users.\footnote{Twitter Safety account announced in a Tweet (see Tweet ID : \href{https://twitter.com/TwitterSafety/status/1379515615954620418}{1379515615954620418}) on April 6, 2021 that their team ``will begin deploying automated tools to build on (their) efforts to label tweets that may contain misleading information around COVID-19 vaccinations".}
